A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 plots/cifar100/aft_comparison.tex

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & -1159.72 & 0.79 & -1159.72 & 0.21 & 0.13 \\
Cox & -- & 0.79 & -- & 0.13 & 0.07 \\
Log Logistic & -1313.15 & 0.78 & -1313.15 & 0.20 & 0.12 \\
Log Normal & -1299.38 & 0.79 & -1299.38 & 0.20 & 0.12 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 124.83 & 0.66 & 124.83 & 0.98 & 0.92 \\
Cox & -- & 0.67 & -- & 0.34 & 0.29 \\
Log Logistic & 80.29 & 0.68 & 80.29 & 0.98 & 0.95 \\
Log Normal & 76.14 & 0.67 & 76.14 & 0.98 & 0.95 \\
\bottomrule
\end{tabular}
\end{table*}
